---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# powers

This is an R package based on the [original version](https://github.com/vincenzocoia/powers) from Vencenzo. 

## What did I do in this assignment?

* I added a family of box-cox transforms, including `box2cox()`, `box2cox_reverse()` and `box2cox_2parameter` to the original `powers` package. 

  `box2cox()` function aims to do a Box-Cox transform.

  `box2cox_reverse()` function aims to do a Box-Cox inverse transform.

  `box2cox_2parameter` function aims to do a Box-Cox transform which contains 2 parameters.

* Document all exported functions.

* Include at least three unit tests for new functions that test common use cases that you anticipate of the function.

* Update the README and vignette to show usage of all the functions in the package.


## Installation

You can install `powers` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("STAT545-UBC-students/hw07-MeiqiYu")
```


## Example

See the [vignette](https://github.com/STAT545-UBC-students/hw07-MeiqiYu/blob/master/vignettes/using_powers.Rmd) for more extensive use, but here's some examples:

```{r example}
powers::box2cox(x=1:6,lambda = 2:7)
powers::box2cox_reverse(x=1:6,lambda = 2:7)
powers::box2cox_2parameter(x=1:5,lambda1 = 0,lambda2 = 4)
```




