---
title: "Using the `powers` package"
author: "Meiqi Yu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". I made it just for teaching purposes.

Want to compute powers without having to use `^` or `**`? Give `sqrt` some friends by loading the `powers` package! 

```{r}
library(powers)
```


## Square, cube reciprocal functions

Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, -0.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
## Use powers instead!
lapply(my_list, square)
```

It even comes with the ability to display its output in plot form!

```{r}
reciprocal(1:10, plot_it=TRUE)
```

Wow!!!

# box-cox transform

We can do box-cox transform easily by `box2cox()`function. Due to the defination of box-cox trandform, x should be positive. In this function, x and lamda should be a vector of the same length, here is an example.

```{r}
box2cox(x=1:6,lambda = 2:7)
```

In some situation, if you enter x of negative values or zero, the function will run by adding a minimum value to x first in order to make x posive. A warning will also appear.

```{r}
box2cox(x=-3:-1,lambda = 2:4)
```

## reverse box-cox transform

Reverse box-cox transform is also available by `box2cox_reverse` function.

```{r}
box2cox_reverse(x=1:6,lambda = 2:7)
```

Similar to `box2cox` function, if the input is not positive, this function will run by adding a minimum value to x first in order to make x posive. A warning will also appear.


```{r}
box2cox_reverse(x=-3:-1,lambda = 2:4)
```

## Two parameter box-cox transform

Two parameter box-cox transform is available by `box2cox_2parameter` function.

If lambda1 is not zero, the output equals to ((x[i]+lambda2)^lambda1 - 1) / lambda1, where x is the input.

```{r}
box2cox_2parameter(x=1:5,lambda1 = 2,lambda2 = 4)
```

If lambda is zero, the output equals to log(x+lambda2)

```{r}
box2cox_2parameter(x=1:5,lambda1 = 0,lambda2 = 4)
```

Similar to the two functions above, if the input is not positive, this function will run by adding a minimum value to x first in order to make x posive. A warning will also appear.

```{r}
box2cox_2parameter(x=-3:-1,lambda1=1,lambda2 = 2)
```












